Minimizing post-shock forecasting error using disparate information

### 2020-07-20 manuscript/manuscript.tex
Overhauled Introduction and Discussion; made minor edits; still need to edit the main text

% title
\title{Minimizing post-shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
\author{Ziyu Liu\thanks{ziyuliu3@illinois.edu}}
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

@@

\begin{center}
  \textbf{Note}
\end{center}

\begin{center}
  \textbf{Updates in this version}
\end{center}

\begin{enumerate}
  \item Revisions to the manuscript (mainly in Simulations and Discussions). The comments are addressed as well.
\end{enumerate}

% table of contents
%\tableofcontents

\newpage

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best. Leave-one-out cross validation with $k$ random  draws is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users the probabilities that this prospective evaluation is consistent with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock.  However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study. One can then combine these past similar shock effects and add them to the present forecast to reduce the overall forecast error. %Then, we discuss some frequently used methodologies that may be applied in this situation.
%When such past similar shock effects exist, one may be able to aggregate the post-shock information from these disparate time series to aid the post-shock forecast for the time series under investigation.

Improving forecasts through forecast combination has a rich history \citep{bates1969combination, mundlak1978pooling, timmermann2006forecast, granger2014forecasting}.  
%\citet{timmermann2006forecast} provided several reasons for combining forecasts.  In particular, combining forecasts may be beneficial when: 1) the information set underlying individual forecasts is often unobserved to the forecast user; 2) different individual forecasts may be very differently affected by non-stationarity and model misspecifications; 3) different individual forecasts may be motivated by different loss functions \citep[and references therein]{timmermann2006forecast}. 
The classical setting for the forecast combination problem is when there are competing forecasts for a single time series.  %In this setting, one may desire combining forecasts as a method for lowering overall forecast error. %\textbf{Integrate this paragraph into the next paragraph.}
In this setting there are a plethora of methods for combining forecasts, e.g., model averaging \citep{newbold2002forecast, hendry2004pooling, koop2004forecasting, timmermann2006forecast, eklund2007forecast, hansen2008least}, model selection \citep{swanson1997model, swanson2001choosing, lee2015model}, and other various methods \citep{pesaran2011forecast,li2014forecasting}. Forecast encompassing methods are developed to test whether competing forecasts are suitable for combinations \citep{newbold2002forecast, fang2003forecasting}.

%Time-series pooling is a broad topic for borrowing information from multiple time series for prediction improvement and is the focus of this paper. \textbf{Need to mention that these methods may fail or be irrelevant in the presence of shock effects.}

% In our post-shock setting we combine estimated quantities from different time series with the aim of lowering forecast error for a single time series under study. Our techniques are similar to those in time-series pooling and data integration.  The literature of time-series pooling is mainly related to pooling cross-sectional panel data \citep{mundlak1978pooling, zellner1991forecasting, fosten2019panel}. The issues about whether to assume homogeneity or heterogeneity of slope coefficients across individual units are confounded. \citet{baltagi2008forecasting} showed that homogeneity approach often outperform  heterogeneity one in mean squared forecast error; while heterogeneity approach is more general to accommodate differences among units. \textbf{How does this relevant to what we are doing?}

Data integration and time series pooling for forecasting is a broad domain of research including ideas from many areas. Time-series pooling methods are frequently used for panel data \citep{zellner1991forecasting, hoogstrate2000pooling, baltagi2008forecasting, fosten2019panel, liu2020forecasting}.  Recent developments in data integration have investigated versatile methods to combine knowledge from multiple datasets for better prediction. %whose ideas are similar to ours. 
For instance, \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration %estimate posterior parameters for Richards model 
to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution.
%, and conditions for predictive improvement are generally hard to know. 
  \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using clustering. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. %From a machine learning perspective, 
\citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool. However, the model-free perspective seeks for a perfect fit on the past data. If the work of \citet{agarwal2020two} were adapted to post-shock setting by treating structural shocks as "interventions", the prediction would have been only a guess. Though their methods are quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.

%Therefore the traditional forecast combination framework may not be of any help.  
%The Bayesian hierarchical approach of \citet{lee2020estimation} may be too sensitive to prior and the hierarchical parametric model setup.

Overall, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock. To combat this problem, we develop and compare aggregation techniques in this post-shock setting based on the idea of data integration. We assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point.

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the risk-reduction propositions and risk-reduction quantities are estimated by parametric bootstrap. These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed. Furthermore, to inform the credibility of this prospective evaluation, we propose a leave-one-out cross validation with $k$ random draws to estimate the performance of the risk-reduction propositions and best consistency of voting the best shock-effect estimators prospectively. Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a shock on March 9th, 2020. The proposed three aggregation techniques work much better than no adjustment in this example. We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts. We now motivate our aggregation techniques.

@@

Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.  Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$. But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased} in plugging it in with replacing $\E{\alpha_1}$. Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative. Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$. For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.90 \times 0.66 = 0.594$ from table \ref{table1}.  In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.

@@

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in Appendix \ref{smfda}. We computed 3 shock-effect estimates. Using the same model that is described in $\mc{M}_{2}$ (see Section \ref{modelsetup}), we computed 3 shock-effect estimates, namely the adjustment  $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and the inverse-variance weighted $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, the fitting result can be described by
\begin{align*}
 \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000) \quad \text{ and } \quad  \norm{\mrm{vec}\big(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\big)}_{4} = 1314.04.
\end{align*}
Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ reports that the $\alpha_1$ is very similar to $\alpha_5$ (November 27, 2014) under the setup of $\mc{M}_2$ and our collected covariates.

@@

Our proposed model in Section \ref{modelsetup} is a simple model with results in Section \ref{properties} easily generalizing to other more complicated models. Our simple AR(1) model can be extended to AR($p$) settings. %for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$. 
Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors. Similarly, LOOCV with $k$ random draws can be adapted to AR($p$). Besides, the functional form for the mean function for $y_{i,t}$ can be extended beyond the linear regression model under $\mc{M}_2$. Multiple shock-effects can be nested within a time series; and time series in the donor pool are allowed be dependent. As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool. 
%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
%This generalization was adopted in Section \ref{forecasting}. In this case, the variance expressions proposed in Section \ref{properties} will not work. However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest. 
Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions with existing first and second moments. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$. We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.

@@

In this manuscript, we have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.  Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $2p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$. However, in applications, it is possible that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.  Moreover, when $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$. However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$. Note that there are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_f$. $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors. In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.

Double bootstrap can be another general bootstrap alternative to the one proposed in Section \ref{varbootstrap}. The double bootstrap procedure adds another layer of residual bootstrapping between resampling of the donor pool and the resampling of the residuals. This procedure enables estimation of the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$. In the framework of double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, we can check whether a bootstrap percentile interval contain 0 at a desired error threshold. We have attempted Monte Carlo simulations using the same setting in Section \ref{simulation} for the double bootstrap procedure, the results of which are quite similar to those of Section \ref{varbootstrap}.

For the use of our methodology, caution should be dedicated to the construction of donor pool. If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.   Moreover, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large. It is  due to the fact that plug-in estimation of  risk-reduction quantities in Section \ref{varbootstrap} gains more precision when $n$ becomes large.

>>>>

% title
\title{Minimizing post-shock forecasting error using disparate information}
\author{Jilei Lin\thanks{jileil2@ilinois.edu}}
\author{Daniel J. Eck\thanks{dje13@illinois.edu}}
\affil{Department of Statistics, University of Illinois at Urbana-Champaign}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best. Leave-one-out cross validation is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users of the probabilities that this prospective evaluation is consistent with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

In this article we provide forecasting adjustment techniques with the goal of lowering overall forecast error when the time series under study has undergone a structural shock. 
%It is unlikely that any forecast that previously gave successful predictions for the time series of interest will be able to accommodate the structural shock. However, all is not lost in this setting, one can integrate information from disparate time series that have previously undergone similar structural shocks to estimate the shock effect of the time series under study. 
The core idea of our methodology is to sensibly combine similar shock effects that have occurred in the past which arose from disparate time-series, and then add them to the present forecast. Our method of combining disparate shock effects embraces ideas from time series pooling using cross-sectional panel data \citep{ramaswamy1993empirical, pesaran1999pooled, hoogstrate2000pooling, baltagi2008forecasting, koop2012forecasting, liu2020forecasting}, judgement forecasting \citep{svensson2005monetary, monti2008forecast}, and synthetic control methodology \citep{abadie2010synthetic, agarwal2020two}, and expectation shocks \citep{croushore2006data, clements2019measuring}. %, and nowcasting \citep{matheson2010nowcasting, fosten2019panel}. %baltagi2008econometric

In our post-shocking setting, the researcher has a time series of interest which is known to have recently undergone a structural shock, and the post-shock response is not observed. The researcher must therefore move beyond the modeling paradigm that they were previously working under to accommodate this new shockas in judgement forecasting \citep{monti2008forecast, svensson2005monetary}. In our methodological framework, the researcher creates a synthetic panel of disparate time series which have undergone similar structural shocks in the past. Construction of the donor pool that forms this panel is similar to that in synthetic control methodology (SCM) \citep{abadie2010synthetic}. As in SCM, care is needed when forming the donor pool of disparate time series. However, there are key differences between our framework and SCM. We assume that the disparate time series are independent from the time series under study before the timing of the shock. We also assume that the shock-effects for each disparate time series are independent realizations from some unknown distribution.

We estimate the shock-effects that are present in the disparate time series for which post-shock responses are observed. We then aggregate these estimated shock-effects and use this aggregated estimate as an estimator for the shock-effect in the time series of interest. This estimator is then added to a forecast for the yet to be realized post-shock response corresponding to the time series of interest. Shock-effects in our post-shock forecasting framework is similar to ``expectation shocks'' which are studied in \cite{clements2019measuring}. The context in \cite{clements2019measuring} allowed for consistent estimation of expectation shocks under a vector autoregressive model, possibly involving an instrumental variable approach as in \cite{croushore2006data}. We offer no such consistency guarantee here. In our context, the yet to observed shock-effect of interest is a realization from a random process that can only be partially explained by the realizations of the disparate time series.

%Therefore the traditional forecast combination framework may not be of any help.  
%The Bayesian hierarchical approach of \citet{lee2020estimation} may be too sensitive to prior and the hierarchical parametric model setup. Overall, it is very unlikely that the above mentioned methods will work ideally since they are trained on the time series data that do not experience such a shock.

In this paper, we will assume a simple auto regressive data generating process similar to that in \citet{blundell1998initial} with a general random effects structure. Therefore, our methodology is similar to the ``$K$ latent pooling'' framework of \cite{ramaswamy1993empirical}. However, our model formulation is more general than \cite{ramaswamy1993empirical} and our donor pool is formed from independent time series.
%The main idea of our methodology is to provide a scalar adjustment, based on estimated shock effects from the disparate time series, which is added to the original forecast at the known shock time point. 
We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}.  These adjustment strategies all ``incorrectly'' target the mean of the shock-effect distribution. However, such an estimation strategy can reduce mean squared error (MSE) when variation in the shock-effect distribution is small relative to the mean. We provide risk-reduction propositions that detail the conditions when the adjusted forecasts will work better than the original forecast. The involved parameters in the risk-reduction propositions and risk-reduction quantities can be estimated by a residual bootstrap procedure that we develop within. %These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques will work well before the post-shock response is observed. 
We also motivate a simple leave-one-out cross validation procedure which can prospectively assess the performance of our shock-effect adjustment estimators without. This prospective assessment does not require the observation of the post-shock response. Our Monte Carlo simulation results show that the risk-reduction conditions are highly consistent when the model for the shock effects is identified well with appropriate covariates under a fixed design. We demonstrate the utility of our methodology in a real data analysis in which we forecast the stock price of Conoco Phillips shares that experienced a large structural shock on March 9th, 2020. We show that our proposed adjustment estimators yield much better results than no adjustment in this setting. We also use this example to demonstrate settings in which the shock-effect may be decomposed into separate estimable parts. We now motivate our framework for post-shock forecasting.

@@

Additionally, we  observe that in most cases $\delta_{\hat{\alpha}_{\rm wadj}}$ reports $\hat{\alpha}_{\rm wadj}$ reduces the risk even when $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}_{\rm wadj}})$ starts to break down.  Recall from Section \ref{varbootstrap} that $\hat{\Delta}(\hat{\alpha})$ contains the squared bias for estimating $\E{\alpha_1}$. But it is not present for $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ since we applied the fact  $\hat{\alpha}_{\rm wadj}$ is unbiased for $\E{\alpha_1}$ from Proposition \ref{unbiased} in plugging it in with replacing $\E{\alpha_1}$. Therefore, when the signal from covariates is poorer, $\delta_{\hat{\alpha}_{\rm wadj}}$ becomes less conservative. Besides, the averaged $I\big(\hat{\Delta}(\hat{\alpha})>0\big)$ times $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ can provide an approximation for the probability that $\hat{\alpha}$ actually reduces the risk assuming an symmetry of consistencies between the cases when $\hat{\Delta}(\hat{\alpha})>0$ and when $\hat{\Delta}(\hat{\alpha})<0$. For example, when $n = 5$ and $\sigma_{\alpha}=50$, the probability that $\hat{\alpha}_{\rm adj}$ reduces the risk is approximately $0.83 \times 0.55 = 0.457$ from Table \ref{table1}.  In other words,  the probability that $\hat{\alpha}$ reduces the risk has the same pattern as $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ has with $n$ and $\sigma_{\alpha}$ for $\hat{\alpha}\in \mc{A}$.

@@

We assume that the five shocks are independent of the shock that Conoco Phillips experienced on March 9, 2020. The covariates and response of time series in the donor pool are adjusted for inflation. Note that there are three shock-effects nested in the time series 2008 September, we assume that these three shocks are independent, where the assumption checks using likelihood ratio test are provided in the Supplementary Materials. Under $\mc{M}_{2}$, we computed $\hat{\alpha}_{\rm adj}$, weighted adjustment $\hat{\alpha}_{\rm wadj}$, and $\hat{\alpha}_{\rm IVW}$. For $\hat{\alpha}_{\rm wadj}$, we observe that 
$
  \mathbf{W}^*= (0.000,0.000, 0.000, 0.000, 1.000)
$
and 
$
  \norm{\mrm{vec}\left(\mbf{X}_1-\hat{\mbf{X}}_1(\mbf{W}^*)\right)}_{4} = 1314.04.
$
Note that the norm is computed using the $k$-dimensional Euclidean metric. The solution $\mathbf{W}^*$ suggests that the shock effect of interest is replicated by the November 27, 2014 shock effect.

@@

We developed methodology for forecasting post-shock response values after the occurrence of a structural. Our methodology is as follows: construct a synthetic panel of disparate time series which have undergone similar shocks, estimate the shock-effects in those series, aggregate them, and then adjust the original forecast by adding the aggregated shock-effect estimator to the original forecast. We provided risk-reduction propositions and empirical tools that can prospectively assess the effectiveness of our adjustment strategies in additive shock-effect settings. The model that we verify these claims under is a simple AR(1) model. Similar results can be obtained for more general models such as AR($p$), vector autoregression, and generalized autoregressive conditional heteroskedasticity models. %for $y_{i,t}$ with an additional component $\alpha_i 1(D_{i,t}=T_i^* + 1)$.

Moreover, the mean function for $\alpha_i$ under $\mc{M}_2$ can be extended to include more lagged predictors. The functional form of the mean function in our considered models can be extended beyond the linear regression model. Multiple shock-effects can be nested within a time series; and time series in the donor pool can be dependent. As an example, we could consider a dependency structure for the September 2008 shock effects in our analysis of Conoco Phillips stock. But we note that consistency estimates from LOOCV with $k$ random draws may not work well if donor pool candidates are not mutually independent since the almost unbiased property hinges on the mutual independence among candidates in the donor pool.
%This generalization is possible since our risk-reduction propositions in Section \ref{properties} assumes the shock-effect estimates are independent of $\alpha_1$, the shock effect for the time series of interest; and allows arbitrary dependence of shock-effects in the donor pool. 
%Specific to this generalization, we edit the model of $\alpha_i$ to $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{3, T_i^* + 1} + \gamma_i'\mathbf{x}_{3, T_i^*} + \tilde{\varepsilon}_i$ for $i = 3, 4, 5$ and $\alpha_i = \mu_{\alpha} + \delta_i'\mathbf{x}_{4, T_i^* + 1} + \gamma_i'\mathbf{x}_{4, T_i^*} + \tilde{\varepsilon}_i$ for $i = 6$.
%This generalization was adopted in Section \ref{forecasting}. In this case, the variance expressions proposed in Section \ref{properties} will not work. However, the risk-reduction propositions in Section \ref{properties} will work  as long as those shock-effects (not necessarily mutually independent) in the donor pool are independent of the one of interest. 
Although it is reflected in $\mc{M}_2$, we stress that our proposed methods allow $\alpha_i$ to follow arbitrary distributions provided that second moments exist. The covariates in the model for $\alpha_i$ under $\mc{M}_2$ can be different from the covariates in the model of $y_{i,t}$. We also note that our post-shock framework can be extended to settings where the shock effect can be decomposed into separable estimable parts. An example of this is the additive shock effect estimators that we studied in our Conoco Phillips analysis.

@@

We have implicitly assumed that $\mathbf{W}^*$ is non-degenerate in the population.  Recall that in Section \ref{constructionofestimators} we noted that if there exists some $\mathbf{W}^*$ which satisfies \eqref{SCM} and $2p < n$, then there will be infinitely many solutions to $\mathbf{W}^*$. However, in applications, it is possible that $\mathbf{W}^*$ may take values on the boundary of $\mc{W}$, in which case bootstrapping may fail to estimate the distribution of $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}.  Moreover, when $2p < n$, $\mc{B}_u$ fails since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$. However, this issue will not occur under $\mc{B}_f$ since it takes $\mbf{W}^*$ as being fixed and the parameter space is $\Theta$ that does not involve the constrained $\mc{W}$. Note that there are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_f$. $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors. In contrast, $\mc{B}_f$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error.

%Double bootstrap can also be employed as an alternative to the bootstrap procedure proposed in Section \ref{varbootstrap}. 
A double bootstrap procedure with similar steps to the bootstrap technique in Section~\ref{varbootstrap} can estimate the distribution of $\hat\Delta(\hat{\alpha})$ for $\hat{\alpha} \in \mc{A}$. The double bootstrap, instead of checking whether $\Delta(\hat{\alpha})>0$, can check whether a bootstrap percentile interval of resampled estimates of $\Delta(\hat{\alpha})$ contain 0 at a desired error threshold. We investigated such a double bootstrap procedure and found that it produced inferences that were similar to those produced using the bootstrap techniques developed in the main text.

There have been several recent time series pooling methods developed for forecasting COVID-19 cases. \citet{lee2020estimation} constructed a Bayesian hierarchical model embracing data integration to improve predictive precision of COVID-19 infection trajectories for different countries. A similar setup may be appropriate for post-shock prediction but may be too dependent upon model specification for the shock distribution. \citet{plessen2020integrated} employed a data-mining approach to combine COVID-19 data from different countries as input to predict global net daily infections and deaths of COVID-19 using a clustering approach. However, there is a tremendous amount of volatility in this form of COVID-19 data, and the fit of this prediction method may be improved with modeling structure or preprocessing of the donor pool. \citet{agarwal2020two} proposed a model-free synthetic intervention method to predict unobserved potential outcomes after different interventions given a donor pool of observed outcomes with given interventions. They also provide useful guidelines for how to estimate the effects of potential interventions by giving recommendations for choosing the metric of interest, the intervention of interest, time horizons, and the donor pool. Although the methodology in \citet{agarwal2020two} is quite general, there is no guarantee for theoretical properties in prediction without assuming any distributional structure.
